Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2021-10-31 docs/00-manuscripts/mdpi/manuscript.tex
Moved l.55 - l.62 to the end of the introduction as suggested by Reviewer2
Add more introductory content for the "tree defoliation" topic

% link to forest health analysis and show exemplary studies

ML methods in combination with remote sensing data are used in many environmental fields such as vegetation cover analysis or forest carbon storage mapping \cite{mascaro2014, urban2018}.
The ability of predicting into unknown space qualifies ML algorithms as a helpful tool for such environmental analyses.
One aspect of this research field is to enhance the understanding of biotic and abiotic stress triggers, for example by analyzing tree defoliation \cite{hawrylo2018}.

Other approaches for analyzing forest health include change detection \cite{zhang2016} or describing the current health status of forests on a stand level \cite{townsend2012}.
In such studies, the defoliation of trees serves as a proxy for forest health by describing the impact of biotic and abiotic pest triggers \cite{townsend2012, goodbody2018}.

@@

% now that we introduced the importance of remote sensing indices for forest health, explain what is new in this study
Despite their popularity in environmental modeling, there are no studies so far which used ML algorithms in combination with remote sensing data to analyze defoliation at the tree level.
This study aims to close this gap by analyzing tree defoliation in northern Spain using airborne hyperspectral data.
The methodology of this study uses ML methods in combination with feature selection and hyperparameter tuning.
In addition, feature importance was analyzed.
Incorporating the idea of creating data-driven \ac{NRI}s, this study also discusses the practical problems of high dimensionality in environmental modeling \cite{trunk1979, xu2016}.

@@

>>>>

% link to forest health (defoliation) analysis and show exemplary studies

ML methods in combination with remote sensing data are used in many environmental fields such as vegetation cover analysis or forest carbon storage mapping \cite{mascaro2014, urban2018}.
The ability of predicting into unknown space qualifies ML algorithms as a helpful tool for such environmental analyses.
One aspect of this research field is to enhance the understanding of biotic and abiotic stress triggers, for example by analyzing tree defoliation \cite{hawrylo2018}.
Defoliation is known to be a proxy for pathogen and insect damage \cite{pollastrini2016}.
While common symptoms are observable across species, some effects and their degree are species-specific \cite{gottardini2020}.
Defoliation has also been shown to increase predisposition of tree death from secondary biotic factors of up to ten years after the actual defoliation event \cite{oliva2016}.
Other approaches for analyzing forest health include change detection \cite{zhang2016} or describing the current health status of forests on a stand level \cite{townsend2012}.

@@

@@

% Explain what is new in this study and link to methodology
Despite their popularity in environmental modeling, there are no studies so far which used ML algorithms in combination with remote sensing data to analyze defoliation at the tree level.
This study aims to close this gap by analyzing tree defoliation in northern Spain using airborne hyperspectral data.
The methodology of this study uses ML methods in combination with feature selection and hyperparameter tuning.
In addition, feature importance was analyzed.
Incorporating the idea of creating data-driven \ac{NRI}s, this study also discusses the practical problems of high dimensionality in environmental modeling \cite{trunk1979, xu2016}.
